UCD\\MSc Thesis Proposal:\\\emph{Real-time Framework For Continuous Capacity Planning in Cloud Environment With Dynamic Pricing}

### 2014-05-14 paper/proposal.tex
methodology added

\title{UCD
\\MSc Thesis Proposal:\\\emph{Real-time System For Continuous Capacity Planning in Cloud Environment With Dynamic Pricing}}
\author{Kamil Smuga}
\date{\today}

@@

\begin{itemize}
  \item Thesis statement: An analysis of current utilization of the infrastructure in terms of price effectiveness in dynamic pricing IaaS model. A calculation of optimal configuration and adjustments based on recent data and future trends calculated from the load. 
  \item Project work: The system will accept incoming data from the IaaS provider with utilisation metrics and a number of running instances for a given type (light, medium, heavy, on demand). The data will be stored, analysed in terms of price optimality (subject for research) and graphed on capacity planning dashboard.
\end{itemize}

{\bf Motivation.} 
\begin{itemize}
  \item New startups often attempt to solve globe wide problems and have to either process increasing amounts of data either gather millions of users. Although the problem of scaling is hard enough by itself, a reality with limited budgets and business sustainability requires to tackle the scaling problem from the most optimal, cost-effective angle. Capacity planning can make a difference between making or losing the money in a dynamic, price variable environment. Based on a dynamic nature of business size and external factors like pricing, the capacity planning needs to be continuously adjusted and become a routine for daily operations. 
  \item Solving the problem of visualisation and optimisation of infrastructure costs will make decisions about pricing and provider choice possible in an educated and more  confident manner. 
\end{itemize}

{\bf Related Work.}
%Demonstrate the connection between your chosen problem and its foundations in existing work. 
\begin{itemize}
  \item What are the key theoretical models (e.g. process-based, formal language/complexity models, probability-based) and algorithms have been applied toward this problem previously? 
  \item What limitation and/or opportunity do you plan to address in your project/thesis?
  \item
In the related research literature, how is success measured (e.g. metrics and/or coverage of problem aspects)?
\end{itemize}

@@

\begin{itemize}
\item For projects, which libraries or software tools will be used for development, and at the highest level, what is the software design?
\item For theory-based projects and theses, what are the key theorems to be developed and/or proven? What proof techniques will be used?
\item For other theses, what algorithms will be adapted or devised, and what algorithms will they be compared with in your experiments?
\end{itemize}

>>>>

\title{UCD\\MSc Thesis Proposal:\\\emph{Real-time Framework For Continuous Capacity Planning in Cloud Environment With Dynamic Pricing}}
\author{Kamil Smuga}
\date{\today}

@@

\begin{itemize}
  \item Thesis statement: An analysis of current utilization of the infrastructure in terms of price effectiveness in dynamic pricing IaaS model. A calculation of optimal configuration and adjustments based on recent data and future trends calculated from the load. 
  \item Project work: The system will accept incoming data from the IaaS provider with utilisation metrics and a number of running instances for a given type (light, medium, heavy, on demand). The data will be stored, analysed in terms of price optimality (subject for research) and graphed on a capacity planning dashboard.  
\end{itemize}

{\bf Motivation.} 
\begin{itemize}
  \item New startups often attempt to solve globe wide problems and have to either process increasing amounts of data either gather millions of users. Although the problem of scaling is hard enough by itself, the reality with limited budgets and business sustainability requires to tackle the scaling problem from the most optimal, cost-effective angle. Capacity planning can make a difference between making or losing the money in a dynamic, price variable environment. Based on a dynamic nature of business size and external factors like pricing, a capacity planning and management need to be continuously adjusted and become an integral part of daily operations. 
  \item Solving the problem of visualisation and optimisation of infrastructure costs will make decisions about pricing and provider choice possible in an educated and more  confident manner.

\end{itemize}

{\bf Related Work.}
%Demonstrate the connection between your chosen problem and its foundations in existing work.

Most of the work in Capacity Planning for Cloud field is conducted from IaaS provider perspective. This paper will focus on SaaS provider who is charged on VM uptime rather than cpu, memory, i/o utlization. Moreover, VM uptime price varies based on renting strategy. This specific problem seems to be somewhat unexplored in the research area.

@@

\begin{itemize}
\item High level software design:
  \begin{itemize}
   \item Input: Uptime and pricing scheme (on-demand, light, medium, heavy) metrics from the host.
   \item Analysis: An algorithm that takes the data and indicates how optimal the usage is for a given pricing configuration.
   \item Output: Send data to graphing system to create a dashboard that shows current usage and optimality ratio
  \end{itemize}
\end{itemize}
